% Vision statement

People all over the world have differing opinion regarding censorship in any commu-
nication medium. Internet, being the most popular communication medium of this
age, has enhanced this dispute. According to Freedom on the Net, Bangladesh is among
the list of countries that have partly free internet. Our project, ISP Cenosrship Analyzer aims to
investigate the existing internet censorship mechanism in Bangladesh.

% Project Goals

\subsection{Project Goals}

	% itemize
	\begin{itemize}
	
	\item To detect whether censorship is applied to a url or a list of urls
	\item To detect which type of censorship is applied to a url or list of urls, if censorship is actually applied.
	\item To analyze the pattern of censorship types over a period of time per user basis.
	\item To help an ISP obtain whether their censorship is correctly applied, in a short amount of time.
	
	\end{itemize}
	
	
% Project Scope
\subsection{Project Scope}
	We classify method of censorship into three broad categories: DNS, TCP, HTTP related censorship.
	In this section, we describe the features a user can use.
	
\subsubsection{Desktop End}
	% Desktop end has a relatively simple GUI, with a few buttons and 
	\begin{itemize}	
		\item Users can create an account in the website using their email, and run tests on a single url or a list of urls (inside a text file).
		\item Users can choose which test type to run for detection (DNS, TCP, HTTP) in their desktop application.
		\item Users can login using their email in the desktop application to send the reports back to the system website server.
		\item Users can view their reports in the desktop application with respect to many filters (eg. within a certain time interval, test type only TCP, on a particular url, etc).
	\end{itemize}

\subsubsection{Website End}
	\begin{itemize}
		\item On the website end, users (after logging in) are introduced to a dashboard showing various data for their past reports (eg. top 5 urls queried by user, percentage of DNS, TCP, HTTP censorships, etc).
		\item On the website end, users will also have a screen to view all their reports (and apply various filtering).
		\item Users will also be able to download the reports in a csv format if they want to run their own custom queries for later use.
	\end{itemize}

	
% Milestones and Deliverables
\subsection{Milestones and Deliverables}
	
	\begin{enumerate}
	    \item Requirement Analysis, Class Diagram, E.R Diagram
	    \item Database Implementation using MySql and Desktop User Interface design.
	    \item DNS Censorship Detection sub-system implementation.
	    \item DNS Censorship Detection sub-system integration with Desktop User Interface.
	    \item TCP Censorship Detection sub-system implementation with Desktop User Interface.
	    \item HTTP Censorship Detection sub-system implementation with Desktop User Interface.
        \item Website Dashboard design and implementation.
        \item Website integration testing with Desktop side and all three test types.
	\end{enumerate}
	
	
	